Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-03 p2/def-commands.tex
Proofs for the rules

TODO DELETE:
As suggested above, we will frequently only investigate
the types of the input and output values of a command
(its input and output types), and write
$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.

@@

\myskip
Depending on their input and output types, there are nine types of commands,
which we separate into four categories depending on the overall effect of the command.
Constructions commands extend the filesystem,
while destruction commands shrink it;
the replacement command replaces a file value with a (presumably different) file value,
and assertion commands either break the filesystem, or assert the type of the value at a node.
\begin{mydef}[Command categories]\mlabel{def:command_categories}
Depending on their input and output types, filesystem commands
belong to exactly one of the following four categories:
\begin{itemize}
\item[]\emph{Construction commands:}
    $\cbfa{n}$, $\cbda{n}$ and $\cfda{n}$;
\item[]\emph{Destruction commands:}
    $\cdfa{n}$, $\cdba{n}$ and $\cfba{n}$;
\item[]\emph{Assertion commands:}
    $\cbba{n}$ and $\cdda{n}$;
\item[]\emph{Replacement command:}
    $\caaa{\valfx}{\valff}{n}$.
\qedhere
\end{itemize}
\end{mydef}

>>>>

@@

\myskip
Depending on their input and output types, there are nine types of commands,
which we separate into four categories depending on the overall effect of the command.
Constructions commands extend the filesystem,
while destruction commands shrink it;
the replacement command replaces a file value with a file value
(which may or may not be different from the original value),
and assertion commands either break the filesystem, or assert the type of the value at a node.
\begin{mydef}[Command categories]\mlabel{def:command_categories}
Depending on their input and output types, filesystem commands
belong to exactly one of the following four categories:
\begin{itemize}
\item[]\emph{Construction commands:}
    $\cbfa{n}$, $\cbda{n}$ and $\cfda{n}$;
\item[]\emph{Destruction commands:}
    $\cdfa{n}$, $\cdba{n}$ and $\cfba{n}$;
\item[]\emph{Assertion commands:}
    $\cbba{n}$ and $\cdda{n}$;
\item[]\emph{Replacement command:}
    $\caaa{\valfx}{\valff}{n}$.
\qedhere
\end{itemize}
\end{mydef}
